---
title: "First Knit"
author: "Eric Soto"
date: "28 Aug 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
print(xx)
#Drive_ltr <- strtrim(xx,2)
#yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
yy = 'Kawhi.jpg'
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="Fun guy")  
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

## Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?  


###my answer     
  
Irrelevent I am sitting at home due to the school being closed for the Corona   
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

###my answer     
  
  Eric is my name but I go by Big Daddy, Im just playing call me Eric
   
 




##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

###my answer     
  
   I would love to make my own life at the end of the day. I think there will be nothing better than just knowing that I am one who worked my way up. I want to get at least my bachelors, and maybe when Im old go back to school again and get another degree.
 




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

###my answer     
  
   No Sir I havent ever been out of the country.If i could go anywhere I would probably go to Japan or England to see the history. I would probably choose the Marines, I say that because I think Its go all on or not at all.
  




##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?
 

###my answer     
  
   I would like to pass with an A im going to try my hardest. I dont think im good at math so whatver the minimum is ill take.
 





##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

###my answer   
  
   
  I am running on a Mac book air but i have no clue how to use it if im being honest. I am straight out of High school, Eastside highschool to be exact . I currently work at del taco as well.




